|

### 2021-12-24 paper/dcpo_demsupport.Rmd
clean up appendices

First, for each item used in the two articles' measure of democratic support, we identified the original variable names and corresponding values in each survey dataset. 
We then used the `dcpo_setup` and `format_claassen` functions of the `DCPOtools` R package [@Solt2019] to automate the process of generating a dataset of survey marginals.
These survey marginals were then used to generate estimates of democratic support in Stan using the `supdem.stan.mod5.stan` script from the @Claassen2020a Dataverse materials.
Draws from the posterior distribution quantify the uncertainty in the estimates.

@@

In Appendix \@ref(moc), we illustrate how we employed these simulated distributions to take uncertainty into account in the models replicating the analyses of [@Claassen2020a; @Claassen2020b].

@@

## Numeric Results for Figure \@ref(fig:plot-fullAJPS) and Figure \@ref(fig:plot-fullAPSR) {-}

During the replications of [@Claassen2020a;@Claassen2020b], we encountered a number of miscodings in the original data that we corrected.
For example, the item "necesitamos un líder fuerte que no tenga que ser eligido" was coded as `strong_lapop_2`, although according to the AmericasBarometer codebooks, this question and that coded as `strong_lapop_1` employed the identical language:

We therefore coded both as `strong_lapop_1`.
Other examples include inconsistent coding regarding what constitutes a "democracy-supporting" response and the inconsistent application of the stated rule regarding "don't know" and other nonresponses.
Here we use the corrected data for the replications with uncertainty to ensure that issues of data quality did not distort the results presented.

Finally, for the GMM models, the original publication presented the observation number based on the trimmed data, i.e., "2435", while the tabulating function in the replication file (line 86) uses the full used-observation number, "4735." 
We follow the replication file in the tables below.

>>>>

First, for each item used in the two articles' measure of democratic support, we identified the original variable names and corresponding values in each survey dataset. 
We then used the `dcpo_setup` and `format_claassen` functions of the `DCPOtools` R package [@Solt2019] to automate the process of generating a dataset of survey marginals.
We encountered a number of miscodings in the original data that we corrected.
For example, the item "necesitamos un líder fuerte que no tenga que ser eligido" was coded as `strong_lapop_2`, although according to the AmericasBarometer codebooks, this question and that coded as `strong_lapop_1` employed the identical language:

We therefore coded both as `strong_lapop_1`.
Other examples include inconsistent coding regarding what constitutes a "democracy-supporting" response and the inconsistent application of the stated rule regarding "don't know" and other nonresponses.
Here we use the corrected data for the replications with uncertainty to ensure that issues of data quality did not distort the results presented.
These survey marginals were then used to generate estimates of democratic support in Stan using the `supdem.stan.mod5.stan` script from the @Claassen2020a Dataverse materials.
Draws from the posterior distribution quantify the uncertainty in the estimates.
Finally, for the GMM models, the original publication presented the observation number based on the trimmed data, i.e., "2435", while the tabulating function in the replication file (line 86) uses the full used-observation number, "4735." 
We follow the replication file in the tables of Appendix \@ref(tables_not_plots) below.

@@

@@

# Numeric Results for Figures \@ref(fig:plot-fullAJPS) and \@ref(fig:plot-fullAPSR) {#tables_not_plots}
